site_map

### 2020-09-20 site_map.Rmd
update

site_map 
```

>>>>

site_map

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) +
  theme_bw() +
  coord_equal() +
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") +
  #geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  geom_rect(data=africa_coast, aes(xmin=15.0, xmax=21.0, ymin=-35.0, ymax=-28.0),  colour = "red", fill = NA, size = 0.75) +
  #annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) +
  theme(panel.border = element_rect(colour = "black", size = 0.4),
        plot.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator")
africa_map

sa_4 <- site_map +
annotation_custom(grob = ggplotGrob(africa_map),
xmin = 17, xmax = 21.4,
ymin = -28.8, ymax = -26.6)
sa_4
```
